---
title: Restocking Ingredients and their location
output:
    html:
        meta:
            css: css/style.css
---


<details>
<summary><b>How to use</b></summary>
<p>
Search for <b>Effect</b> and <b>Location</b> to see what restocking merchants are nearby.
    <ul>
    <li>Type into a column search element to search in that column.</li>
    <li>Type into a global search element to search globally.</li>
    <li>Click on the waffle menu to show/hide columns (restock Count, Weight, or Cost)</li>
    <li>Use <b>;</b> as a separator to search for multiple effects</li>
    </ul>

<b>Examples</b>
    <ul>
    <li>There are two merchants stocking <b>Fortify Fatigue</b> ingredients in <b>Vivec</b></li>
    <li>There is only a single ingredient, Saltrice, having both <b>Restore Health</b> and <b>Restore Fatigue</b> effects (searching for <i>Restore Health;Restore Fatigue</i>)
    </ul>
</p>

</details> 


```{r, echo = FALSE}
litedown::vest(
    css = c("@npm/simple-datatables/dist/style", "@npm/simple-datatables/dist/column_filter"),
    js = "@npm/simple-datatables"
    )
```

::: {#restocking}
```{r, echo = FALSE}
csv = "restocking.csv"
if(!file.exists(csv)){
    source("src/get_restocking_ingredients.r")
    restocking = get_restocking_ingredients()
    write.csv(restocking, csv, row.names = FALSE)
    } else {
    restocking = read.csv(csv)
    }

names(restocking) = tools::toTitleCase(names(restocking))

# Sort
I(restocking[c("Ingredient", "Effect", "Merchant", "Location", "Count", "Weight", "Value")])
```
:::

```{js, type = "module", echo = FALSE}
let dataTable = new simpleDatatables.DataTable("#restocking > table", {
    perPage: 20,
    perPageSelect: [5, 10, 20, 50, ["All", 0]],
    searchItemSeparator: ";",
    searchQuerySeparator: ";",
    columns: [
        {select: [4, 5, 6], hidden: true}
        ],
    tableRender: (_data, table, type) => {
        if (type === "print") {
            return table
        }
        const tHead = table.childNodes[0]
        const filterHeaders = {
            nodeName: "TR",
            childNodes: tHead.childNodes[0].childNodes.map(
                (_th, index) => ({nodeName: "TH",
                    childNodes: [
                        {
                            nodeName: "INPUT",
                            attributes: {
                                class: "datatable-input",
                                type: "search",
                                "data-and": "true",
                                "data-columns": `[${index}]`
                            }
                        }
                    ]})
            )
        }
        tHead.childNodes.push(filterHeaders)
        return table
        }
    });

window.dataTable = dataTable;
window.columnFilter = simpleDatatables.addColumnFilter(
    dataTable
);
```
